Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars

### 2018-09-11 main.tex
removed bold changes from last revision. draft of changes for this final revision

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation. Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single black dot.}
\label{fig:panel_x}
\end{figure*}

@@

\textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations. Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, can be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}. Our current model does not include this contribution. To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https://grackle.readthedocs.io/en/latest/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) and initial temperature of 10$^{4}$~K for 200~Myr. In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background. As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate. In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left). A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.}

\textbf{We follow up on the qualitative conclusions of these models by running four full-physics simulations, but with no star formation, at the four points starred in the diagram. These vary the radiation bands by factors of 100 each, which is comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}). Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9. Applying both scale factors gives a reduction of 7.9. Thus, we see that the difference between the more realistic case in which both rates increase by the same factor, and the case assumed in the simulations, is only about 20\%.}

@@

\textbf{H$^-$ photodetachment arises from lower energy photons, above 0.76~eV, with a peak in effectiveness around 2~eV. For this reason, low mass stars may contribute significantly, if not dominate, the radiation field responsible for this reaction. The Lyman-Werner radiation field is dominated by short-lived massive stars, with some contribution from older stars up to a few hundred Myr, and is thus subject to significant fluctuations, particularly in periods of no star formation. During these times, H$^-$ photodetachment from low energy photons may play a non-negligible role in regulating H$_2$ formation. Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars. Doing so in our current model, applying an optically thin $1/R^2$ field for each star, would be computationally challenging due to the dramatic increase in the number of stars whose radiation would need to be tracked.}

\textbf{As emphasized in Section~\ref{sec:molecular gas content}, further work modeling low-metallicity dwarf galaxies with a more detailed chemistry model would be useful to clarify the role of various competing phenomena in driving the molecular properties of these galaxies.}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation. Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single white dot.}
\label{fig:panel_x}
\end{figure*}

@@

As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations. Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, can be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}. Our current model does not include this contribution. To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https://grackle.readthedocs.io/en/latest/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) and initial temperature of 10$^{4}$~K for 200~Myr. In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background. As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate. In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left). A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.

We follow up on the qualitative conclusions of these models by running four \textbf{hydrodynamics} simulations, but with no star formation, at the four points starred in the diagram. These vary the radiation bands by factors of 100 each, which is comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}). Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9. Applying both scale factors gives a reduction of 7.9. Thus, we see that the difference between the more realistic case in which both rates increase by the same factor, and the case assumed in the simulations, is only about 20\%.

@@

H$^-$ photodetachment arises from lower energy photons, above 0.76~eV, with a peak in effectiveness around 2~eV. For this reason, low mass stars may contribute significantly, if not dominate, the radiation field responsible for this reaction. The Lyman-Werner radiation field is dominated by short-lived massive stars, with some contribution from older stars up to a few hundred Myr, and is thus subject to significant fluctuations, particularly in periods of no star formation. During these times, H$^-$ photodetachment from low energy photons may play a non-negligible role in regulating H$_2$ formation. Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars. Doing so in our current model, applying an optically thin $1/R^2$ field for each star, would be computationally challenging due to the dramatic increase in the number of stars whose radiation would need to be tracked.

\textbf{Although the lack of star formation in these models produced qualitatively different galaxy properties, these represent simulations with maximal H$_2$ formation. We demonstrate that, even in this case, there is not a dramatic change in the total H$_2$ formation and that the effect of varying the H- photodetachment rate is sub-dominant to other factors. Therefore, we do not expect that ignoring this component of the stellar radiation field to have a significant dynamical impact on our galaxy evolution.}

As emphasized in Section~\ref{sec:molecular gas content}, further work modeling low-metallicity dwarf galaxies with a more detailed chemistry model would be useful to clarify the role of various competing phenomena in driving the molecular properties of these galaxies.
